Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-12-09 rCode/Draft v2.Rmd

---
title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
author: 'Catherine Darin and Zagreb Mukerjee'
date: '11/29/2021'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

\renewcommand{\arraystretch}{1.1}
\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{3}
\setcounter{totalnumber}{4}

@@

@@

@@

# find the predicted democratic vote share
model_input$P_ddem_1 <- model_results$fitted.values

>>>>

---
title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
author: 'Catherine Darin and Zagreb Mukerjee'
date: '11/29/2021'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---
\renewcommand{\arraystretch}{1.1}
\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{3}
\setcounter{totalnumber}{4}

@@

### 04 to 15

@@

\newpage

### 12 to 15

# load map
model_input <- readRDS("../input_12_16.rds")

ggplot() +
  geom_sf(data = mapping_county, aes(fill = ntile_mfg),
          color = NA, size = .01) +
  scale_fill_manual(values = colors,
                    labels = labels) +
  # add state lines
  geom_sf(data = state_shape, fill = NA, color = "black", size = .1) +
  coord_sf(datum = NA) +
  theme_minimal() +
  # geom_sf_text_repel(aes(label = state), data = mapping_small,
  #                    force = .00001,  seed = 10,
  #                    size = 2.5) +
  theme(  axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          text = element_text(size = 8)) +
  labs(title = "Figure 2: Net Change in Manufacturing Employment from 2012 to 2015",
       subtitle = "Normalized by 2011 Overall Employment Levels",
       fill = "Cumulative Change in Manufacturing\nEmployment (2012-2015) per\n2011 Worker")

@@
